% Bachelor in electronics
% double degree, Master in computer embedded systems
% Thesis, combination of embedded, software dev and security
% Worked in automotive sector in embedded linux system
% Research assistant, 3 different tasks
% Capacity to collaborate
% Capacity to manage my own time
% Capacity to learn new topics, research google
% Capacity to work on multiple and tasks
% Capacity to work under pressure with tight deadlines.
\lettersection{Background.}
During my bachelor's degree in Electronic Engineering at the University of Antioquia I had the opportunity to explore several sub-fields of electronics, and the one that intrigued me the most was digital systems. I decided to push my education further and joined the double degree program with the Politecnico di Torino, where I obtained my M.Sc. in Computer Engineering, with focus on Embedded Systems.
For my thesis, I developed a software application for secure passwords storage, that leveraged heavily on the capabilities of the SEcube framework, an open source security-oriented hardware platform with an accompanying set of software libraries.
After graduating, I was hired as a software developer for an automotive infotainment project at Marelli, where I was able to hone my skills in embedded software development in C/C++ within a Linux ecosystem.
Three years later I started my path as researcher at Politecnico di Torino. Over the past year, I have been working on three different projects, two of which focus on bioinformatics algorithms and technologies, and the third on heterogeneous architectures. In addition to my research, I am also serving as a teaching assistant in the computer engineering department.
Thanks to all of these experiences I have improved not only my hard skills, but I have also learned to collaborate with clients, colleagues and students, and to manage my own time and work under pressure with tight deadlines. I have become comfortable with multitasking as well as with investigating on my own new topics that I am not familiar with. I have learned to explain myself better and to support others as well as to ask for help when I need it.
