%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventrySimple
    {Embedded Software Developer} % Job title
    {Teoresi S.p.A | Marelli S.p.A } % Organization
    {Turin, Italy} % Location
    {Oct. 2018 - Dec. 2021} % Date(s)
  \cvtext{
    I worked on-site at Marelli (as a consultant from Teoresi) in the automotive
    infotainment project TBM2, and its evolution TBM20H.
    The main activities I carried out were:
    \begin{cvitems2}
      \item Embedded software design and development.
      \item Code debugging and maintenance.
      \item Front desk analysis.
      \item General engineering support.
      \item Mediation with clients and providers.
    \end{cvitems2}
    During this job I gained experience in:
    \begin{cvitems2}
      \item C++ and C development in an embedded linux environment.
      \item Linux OS and Bash scripting.
      \item Source code management in large projects with Git.
      \item Yocto cross-compilation tools.
      \item Wireless modules for embedded systems (Modem and SIM).
      \item The Legato framework for embedded systems.
      \item Automotive ecosystem (CAN network, AVB audio interface, DLT logging and debugging, emergency call standards).
      \item Atlassian suite for collaboration in large projects (JIRA, Stash, Confluence).
      \item Software requirements and architecture (Rational DOORs, Enterprise architect).
    \end{cvitems2}
  }
%---------------------------------------------------------
\end{cventries}



